Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-06-12 paper-v1.tex
references related work

\subsection{Related work} Some mild attempts to credit peer review has been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials.
\newline It's also worth mentioning \emph{Publons}\cite{Publons}, a service integrated with ORCID (researcher identifier) that provides peer-review metric; \emph{Peerage} of Science\cite{Peerage} and \emph{ResearchSquare}, a journal-independent free service for scientific peer review and publishing that provides also a peer-review of the reviews.
\emph{ScienceMiles} \cite{ScienceMiles} proposes a cryptocurrency for incentivizing peer-reviews through a blockchain-based platform and an open peer-review process. \emph{INFINITCODEX (I8X)} \cite{I8X}, is a platform that promotes cooperative user behaviour through dynamic research papers that undergo  continuous peer review process. The system implements cryptoeconomical incentives for building reputation in the community of users.

@@

% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{ref1-intro.bib,ref2-peerreview.bib,ref2-related.bib, ref3-system.bib,ref4-discuss.bib}

>>>>

\subsection{Related work} Some mild attempts to credit peer review has been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials.
\newline It's also worth mentioning \emph{Publons}\cite{Publons}, a service integrated with ORCID (researcher identifier) that provides peer-review metric; \emph{Peerage} of Science\cite{Peerage} and \emph{ResearchSquare}, a journal-independent free service for scientific peer review and publishing that provides also a peer-review of the reviews. Spearpoint\cite{ResearchCoin} proposes \emph{r-coin} (for ‘ReviewCoin’ or ‘ResearchCoin’), a cryptocurrency that researchers earn for undertaking peer-reviews and that can used to pay for publication fees. \emph{ScienceMiles} \cite{ScienceMiles} is a cryptocurrency for incentivizing peer-reviews through a blockchain-based platform and an open peer-review process. Avital \cite{AvitalToken} suggests a token-based peer-review payment system. \emph{INFINITCODEX (I8X)} \cite{I8X}, is a platform that promotes cooperative user behaviour through dynamic research papers that undergo  continuous peer review process. The system implements cryptoeconomical incentives for building reputation in the community of users. \newline Other proposals to improve the peer-review system have instead focused on features such as decentralization, security \cite{Pevo,CryptSubmit,MarsChain}.

@@

% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{ref1-intro.bib,ref2-peerreview.bib,ref2-relatedwork.bib, ref3-system.bib,ref4-discuss.bib}
